---
title: "Beta_diversity"
output:
  html_document:
    df_print: paged
---



```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(betapart)
```

```{r}
med <- read.csv("../Data/Med_cyano_list_20191204.csv", row.names = NULL)
med <- med %>% 
  filter(Med_border == "yes")
colnames(med)[1] <- "A/A"
med <- med %>% 
  mutate(continent = case_when(Country %in% c("Greece", "Italy", "Spain", "France", "Albania", "Montenegro", "Slovenia", "Portugal", "Bulgaria", "Croatia") ~ "Europe",
                               Country %in% c("Egypt", "Morocco", "Tunisia", "Libya", "Algeria", "Israel","Lebanon") ~ "Africa",Country == "Turkey" ~ "Asia"))
```

#Split habitat types and get Currentname in each of them

```{r}
s <- split(med, med$Habitat_type)
s

couiso_unique <- sapply(s, function(x){
  unique(x["Currentname"])
})
couiso_unique
```

# Select only habitat Pond and spread function
## Get beta diversity

```{r}
pondbeta <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Pond"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) %>% column_to_rownames("Isolationsource")
pondbeta


## Beta diversity between the same habitat, Pond
pondbetapart <- pondbeta
pondbetapart[pondbetapart >= 1] <- 1
pondbetapart <- betapart.core(pondbetapart)
pondbetapart


pondbetapart_pair_jac <- beta.pair(pondbetapart, index.family = "jac")
pondbetapart_pair_jac

# Computing multiple-site dissimilarities, with Jaccard and Sorensen indexes
pondbetapart_multi_jac <- beta.multi(pondbetapart, index.family = "jac")
pondbetapart_multi_jac

pondbetapart_multi_sor <- beta.multi(pondbetapart, index.family = "sor")
pondbetapart_multi_sor
```

# Select only habitat Lake and use the spread function
## Get beta diversity

```{r}
lakebeta <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Lake"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) %>% column_to_rownames("Isolationsource")
#lakebeta <- lakebeta[, -2]
lakebeta

lakebetapart <- lakebeta
lakebetapart[lakebetapart >= 1] <- 1
lakebetapart <-lakebetapart[,-1]

lakebetapart <- betapart.core(lakebetapart)


# Computing multiple-site dissimilarities, with Jaccard and Sorensen indexes
lakebetapart_multi_jac <- beta.multi(lakebetapart, index.family = "jac")
lakebetapart_multi_jac

lakebetapart_multi_sor <- beta.multi(lakebetapart, index.family = "sor")
lakebetapart_multi_sor

```

# Select only habitat Reservoir and spread function
## Get beta diversity

```{r}
resebeta <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Reservoir"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) %>% column_to_rownames("Isolationsource")
#lakebeta <- lakebeta[, -2]
resebeta
  
resebetapart <- resebeta
resebetapart[resebetapart >= 1] <- 1
resebetapart <- betapart.core(resebetapart)
resebetapart

# Computing multiple-site dissimilarities, with Jaccard and Sorensen indexes
resebetapart_multi_jac <- beta.multi(resebetapart, index.family = "jac")
lakebetapart_multi_jac

resebetapart_multi_sor <- beta.multi(resebetapart, index.family = "sor")
resebetapart_multi_sor
```



```{r}
rivbeta <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "River"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) %>% column_to_rownames("Isolationsource")
rivbeta <- rivbeta[, -1]
rivbeta

  
rivbetapart <- rivbeta
rivbetapart[rivbetapart >= 1] <- 1
rivbetapart <- betapart.core(rivbetapart)

rivbetapart_multi_jac <- beta.multi(rivbetapart, index.family = "jac")
rivbetapart_multi_jac

## Save the list in a csv file
capture.output(rivbetapart, file = "rivbetapart.csv")
```



```{r}
streambeta <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Stream"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) %>%  column_to_rownames("Isolationsource") 
#lakebeta <- lakebeta[, -2]
streambeta

  
streambetapart <- streambeta
streambetapart[streambetapart >= 1] <- 1
streambetapart <- betapart.core(streambetapart[, -1])
streambetapart

# Computing multiple-site dissimilarities, with Jaccard and Sorensen indexes
streambetapart_multi_jac <- beta.multi(streambetapart, index.family = "jac")
streambetapart_multi_jac

streambetapart_multi_sor <- beta.multi(streambetapart, index.family = "sor")
streambetapart_multi_sor
```

# Alpha diversity of habitats

```{r}
habspec<- med %>%  
  select(Currentname, Isolationsource, Order) %>% 
  filter(Order != "") %>% 
  group_by(Isolationsource) %>% 
  summarise(N = n()) %>% 
  arrange(desc(N))
habspec
```

```{r}
pondspr<- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Pond"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Isolationsource, N, fill = 0, convert = FALSE, sep = NULL)
pondspr

apply(pondspr[, -1] > 0, 2, sum)
```

# Alpha diversity of habitat Lake

```{r}
lakespr<- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Lake"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Isolationsource, N, fill = 0, convert = FALSE, sep = NULL)
lakespr

apply(lakespr[, -1] > 0, 2, sum)
```


# Menhinick's index is simply the number of species (n) divided by the square-root of the total number of individuals (N).   D=n/√N

```{r}
n <- apply(pondspr[, -1]>0, 2, sum)
N <- apply(pondspr[, -1]>0, 2, sum)
Mehi <- n/sqrt(N)
Mehi
```

#Margalef's index is the number of species (n) minus 1 divided by the natural logarithm of the total number of individuals (N). D= (n−1)log(N)

```{r}
n <- apply(pondspr[, -1]>0, 2, sum)
N <- apply(pondspr[,-1]>0, 2, sum)
Margal <- (n-1)/log(N)
Margal
```



```{r}
lake_species <- med %>% 
  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Lake"))) %>% 
  group_by(Isolationsource) %>% 
  summarise(N = n()) %>% 
  arrange(desc(N))
lake_species <- head(lake_species, 10) %>%
  spread(Currentname, N, full = 0, convert = FALSE, sep = NULL)

```

# Compute total dissimilarity across all n sites, Sorensen and Jaccard indexes implementation of betapart package

```{r}
sore <- med %>% select(Isolationsource, Currentname, Order) %>% 
  filter(Order != " ") %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) 

sore_pa <- sore
sore_pa[sore_pa >=1] <- 1
sore_pa
s <-beta.multi(sore_pa[,-1],index.family = "sorensen")
s

j <- beta.multi(sore_pa[,-1], index.family = "jaccard")
j
```



```{r}
sore <- med %>% select(Isolationsource, Currentname, Order) %>% 
  filter(Order != " ") %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) 


sore_pair <- sore
sore_pair[sore_pair >=1] <- 1
sore_pair

beta.pair(sore_pair[,-1], index.family = "sorensen")
beta.pair(sore_pair[, -1], index.family = "jaccard")

beta.sample(sore_pair[,-1], index.family = "sorensen", samples = 10)
```


```{r}
hab_taxa <- med %>%  filter(Order != "") %>% 
  select(Currentname, Habitat_source) %>% 
  group_by(Currentname, Habitat_source) %>% 
  summarize(N=n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) %>% column_to_rownames("Habitat_source")
hab_taxa[hab_taxa>1] <- 1
hab_taxa
glimpse(hab_taxa)

beta.pair(hab_taxa, index.family = "jaccard")


hab_taxa_dist <- dist(hab_taxa,method = "binary", diag = TRUE)
hab_taxa_clust <- hclust(hab_taxa_dist, method = "average")
plot(hab_taxa_clust)

hab_taxa_clust2 <- hclust(hab_taxa_dist, method = "complete")
plot(hab_taxa_clust2)

hab_taxa_clust3 <- hclust(hab_taxa_dist, method = "ward.D")
plot(hab_taxa_clust3)

hab_taxa_clust3 <- hclust(hab_taxa_dist, method = "ward.D2")
plot(hab_taxa_clust3)


hab_taxa_clust5 <- hclust(hab_taxa_dist, method = "single")
plot(hab_taxa_clust5)

unique(med$Currentname)
unique(med$Family)
unique(med$Genustotal)
```





