---
title: "diversity_indices"
author: "Vica"
date: "10/23/2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r include=FALSE, echo=FALSE}
library(vegan)
library(tidyverse)
```

# Rarefaction with dataset BCI - EXAMPLE

```{r echo=FALSE, include=FALSE}
data(BCI)
S <- specnumber(BCI)  # observed number of species
raremax <- min(rowSums(BCI))
Srare <- rarefy(BCI, raremax)
plot(S, Srare, , xlab = "Obs No of species", ylab = "Rarefied number of species") + abline (0, 1)
rarecurve(BCI, step = 20, sample = raremax, col = "red", cex = 0.6)


sha <- diversity(BCI, "simpson")
H <- diversity(BCI)
```

# Accumulation model with dataset BCI - EXAMPLE

```{r echo=FALSE, include=FALSE}
pool <- poolaccum(BCI)
summary(pool, display =  "chao")
plot(pool)

sac <- specaccum(BCI)
sac
```



```{r}
data(BCI)
opar <- par(mfrow = c(2,2))
plot(contribdiv(BCI, "richness"), main = "Absolute")
plot(contribdiv(BCI, "richness", relative = TRUE), main = "Relative")
plot(contribdiv(BCI, "simpson"))
plot(contribdiv(BCI, "simpson", relative = TRUE))
par(opar)
```

# Insert my dataset

```{r}
med <- read.csv("../Data/Med_cyano_list_20191024.csv", row.names = NULL)
med <- med %>% 
  filter(Med_border == "yes")
colnames(med)[1] <- "A/A"
med <- med %>% 
  mutate(continent = case_when(Country %in% c("Greece", "Italy", "Spain", "France", "Albania", "Montenegro", "Slovenia", "Portugal", "Bulgaria", "Croatia") ~ "Europe",
                               Country %in% c("Egypt", "Morocco", "Tunisia", "Libya", "Algeria", "Israel","Lebanon") ~ "Africa",Country == "Turkey" ~ "Asia"))
```


```{r }
species.number <- med %>% 
  filter(Order != "") %>% 
  select(Order, Country, Currentname) %>% 
  group_by(Country, Currentname) %>% 
  summarize(N = n()) %>% 
  spread(Currentname, N, fill=0, convert = FALSE, sep = NULL) %>%  column_to_rownames("Country")
species.number

species.number.accum <- specaccum(species.number)
species.number.accum
```

# Shannon-Wiener diversity index for each Country

```{r}
species.number.sha <- diversity(species.number, index = "shannon")
species.number.sha
species.number.sha <- as.data.frame(species.number.sha)
species.number.sha
```

# Simpson diversity index 1 - D

```{r}
species.number.simp <- diversity(species.number, "simpson")
species.number.simp
species.number.simp <- as.data.frame(species.number.simp)
species.number.simp
```

# Simpson diversity index 1/D

```{r}
species.number.invsimp <- diversity(species.number, "inv")
species.number.invsimp <- as.data.frame(species.number.invsimp)
species.number.invsimp
```

# Unbiased diversity Simpson index

```{r}
species.number.unbias.simp <- rarefy(species.number, 2) -1
species.number.unbias.simp
```

# Fisher diversity

```{r}
species.number.alpha <- fisher.alpha(species.number)
species.number.alpha <- as.data.frame(species.number.alpha)
species.number.alpha
```

# plot diversity indices Shannon, Simpson, Unbiased Simpson, Fisher alpha

```{r}
diver_plot <- pairs(cbind(species.number.sha, species.number.simp, species.number.invsimp, species.number.alpha), pch = "+", col ="red")

```

# Species richness

```{r}
species.number.rich <- specnumber(species.number, MARGIN = 1)
species.number.rich
```



```{r include = FALSE, echo=FALSE}
taxa.number <- med %>% 
  filter(Family != "") %>% 
  select(Isolationsource, Currentname) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n()) %>% 
  spread(Currentname, N, fill=0, convert = FALSE, sep = NULL)

taxa.number <- column_to_rownames(taxa.number, "Isolationsource")


genus.number <- med %>% 
  filter(Family != "") %>% 
  select(Isolationsource, Currentname) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n()) %>% 
  spread(Currentname, N, fill=0, convert = FALSE, sep = NULL)

genus.number <- column_to_rownames(genus.number, "Isolationsource")


taxa.number.rich <- specnumber(taxa.number, MARGIN = 1)
genus.number.rich <- specnumber(genus.number, MARGIN = 1)
plot(taxa.number.rich, genus.number.rich)
```



```{r include=FALSE, echo=FALSE}
Lat <-med %>% filter(DD_Lat != 0.00) %>% 
  select(Currentname, DD_Lat) %>% 
  group_by(DD_Lat) %>% 
  summarize(N = n()) %>% 
  arrange(DD_Lat)
plot(Lat$N, Lat$DD_Lat)
```

# Contribution diversity approach, based in the differentiation of within-unit and among-unit diversity by using additive diversity partitioning and unit distinctiveness


```{r}
opar <- par(mfrow = c(2,2))
plot(contribdiv(species.number, "richness", scaled = TRUE), main = "Absolute")
plot(contribdiv(species.number, "richness", scaled = TRUE, relative = TRUE), main = "Relative")
plot(contribdiv(species.number, "simpson", scaled = TRUE))
plot(contribdiv(species.number, "simpson", scaled = TRUE, relative = TRUE))
par(opar)
```


```{r include=FALSE, echo=FALSE}
plot(contribdiv(species.number, "richness", scaled = TRUE), main = "Absolute", drop.zero = TRUE)
```


```{r include=FALSE, echo=FALSE}
plot(contribdiv(species.number, "richness", relative = TRUE, scaled = TRUE), main = "Relative")

```


```{r include=FALSE, echo=FALSE}
species.isolat <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Pond"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) %>% 
  column_to_rownames("Isolationsource")
species.isolat

```


```{r include=FALSE, echo=FALSE}
species.isolat.beta.ind <- betadiver(species.isolat, order = TRUE)
species.isolat.beta.ind
```


```{r}
med.habi <- med %>% 
  select (Order, Currentname, Habitat, Habitat_type) %>% 
  filter(Order != "") %>% 
  group_by(Habitat, Currentname) %>% 
  summarize(N = n_distinct(Habitat)) %>% spread(Currentname, N, fill = 0) %>% 
  column_to_rownames("Habitat")

med.habi[med.habi >= 2] <- 1
med.habi 

med.habi.j <- betadiver(med.habi, "j")
med.habi.j
```

# The 24 beta diversity indices by Koleff et al. 2013 for presence-absence data

```{r}
betadiver(help = TRUE)
```

# Whittaker

```{r include = FALSE, echo=FALSE}
species.isolat.w <- betadiver(species.isolat, "w")
species.isolat.w

```


```{r include = FALSE, echo=FALSE}

species.isolat.3 <- betadiver(species.isolat, "-3")
species.isolat.3
```


```{r include = FALSE, echo=FALSE}

species.isolat.2 <- betadiver(species.isolat, "-2")
species.isolat.2
```

# Jaccard dissimilarity index (the most robust when undersampling occurs, according to Schroeder et al. 2018)

```{r}
species.isolat.j <- betadiver(species.isolat, "j")
species.isolat.j
```

# Cody index, one of the most robust presence-absence based indices, according to Schroeder et al. 2018

```{r}
species.isolat.c <- betadiver(species.isolat, "c")
species.isolat.c
```



