---
title: "betapart_Habitat"
author: "Vica"
date: "11/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(betapart)
library(tidyverse)
library(mapproj)
library(vegan)
```


```{r}
med <- read.csv("../Data/Med_cyano_list_20191024.csv", row.names = NULL)
med <- med %>% 
  filter(Med_border == "yes")
colnames(med)[1] <- "A/A"
med <- med %>% 
  mutate(continent = case_when(Country %in% c("Greece", "Italy", "Spain", "France", "Albania", "Montenegro", "Slovenia", "Portugal", "Bulgaria", "Croatia") ~ "Europe",
                               Country %in% c("Egypt", "Morocco", "Tunisia", "Libya", "Algeria", "Israel","Lebanon") ~ "Africa",Country == "Turkey" ~ "Asia"))

med <- med %>% 
mutate(lat_range = case_when(DD_Lat < 30 ~ "Low", DD_Lat > 30 & DD_Lat < 40 ~ "Medium",
                             DD_Lat > 40 ~ "High"))
med
```

# Dataset with Habitats as rows and taxa as columns
## Checking the partitioning beta diversity (turnover + nestedness)

```{r}
med.habi <- med %>% 
  select (Order, Currentname, Habitat, Habitat_type) %>% 
  filter(Order != "") %>% 
  group_by(Habitat, Currentname) %>% 
  summarize(N = n_distinct(Habitat)) %>% spread(Currentname, N, fill = 0) %>% 
  column_to_rownames("Habitat")

med.habi[med.habi >= 2] <- 1
med.habi 

# Computing the basic quantities needed for the multiple-site beta diversity measures

med.habi.core <- betapart.core(med.habi) 
med.habi.core

#Computing the total dissimilarity across all habitats, Jaccard index

med.habi.core.multij <- beta.multi(med.habi.core, index.family = "jaccard") #bJTU component of turnover
med.habi.core.multij

#Computing the total dissimilarity across all habitats, Sorensen index

med.habi.core.multis <- beta.multi(med.habi.core, index.family = "sorensen")
med.habi.core.multis

```



```{r}
med.habi.samp.sor <- beta.sample(med.habi.core, samples = 100, index.family = "sorensen")
med.habi.samp.jac <- beta.sample(med.habi.core, samples = 100, index.family = "jaccard")
med.habi.samp.jac
med.habi.samp <- beta.sample(med.habi.core, samples = 100)
```



```{r}
med.habi.dist <- med.habi.samp$sampled.values 
plot(density(med.habi.dist$beta.SOR), xlim = c(0, 2), ylim = c(0,10), xlab = "Beta diversity", main = "", lwd = 3)+
lines(density(med.habi.dist$beta.SNE), lty = 1, lwd = 2) + lines(density(med.habi.dist$beta.SIM), lty = 2, lwd = 2)

# Computing the same dissimilarity metrics as above ( can be used e.g. Mantel tests, cluster analysis)

med.habi.pair <- beta.pair(med.habi) # can be impemented in other analyses like cluster

plot(hclust(med.habi.pair$beta.sim, method = "average"), hang = -1, main = "", sub = "", xlab = "")
plot(hclust(med.habi.pair$beta.sne, method = "average"), hang = -1, main = "", sub = "", xlab = "")
plot(hclust(med.habi.pair$beta.sor, method = "average"), hang = -1, main = "", sub = "", xlab = "")
```

# Dataset with Habitats as rows and taxa as columns -->  Low latitude
## Checking the partitioning beta diversity (turnover + nestedness)

```{r}
low.lat <- med %>% 
  select(Order, Currentname, Isolationsource, lat_range) %>% 
  filter(Order != "", lat_range == "Low") %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n_distinct(Isolationsource)) %>% spread(Currentname, N, fill = 0) %>% 
  column_to_rownames("Isolationsource")
  low.lat
  
low.lat.core <- betapart.core(low.lat) 
low.lat.core

low.lat.core.multij <- beta.multi(low.lat.core, index.family = "jaccard")
low.lat.core.multij
low.lat.core.multis <- beta.multi(low.lat.core, index.family = "sorensen")
low.lat.core.multis
```

```{r}
low.lat.samp.sor <- beta.sample(low.lat.core, samples = 100, index.family = "sorensen")
low.lat.samp.jac <- beta.sample(low.lat.core, samples = 100, index.family = "jaccard")
low.lat.samp.jac
low.lat.samp <- beta.sample(low.lat.core, samples = 100)
```

```{r}
low.lat.dist <- low.lat.samp$sampled.values 
plot(density(low.lat.dist$beta.SOR), xlim = c(0, 2), ylim = c(0,40), xlab = "Beta diversity", main = "", lwd = 3)+
lines(density(low.lat.dist$beta.SNE), lty = 1, lwd = 2) + lines(density(low.lat.dist$beta.SIM), lty = 2, lwd = 2)

low.lat.pair <- beta.pair(low.lat)
plot(hclust(low.lat.pair$beta.sim, method = "average"), hang = -1, main = "", sub = "", xlab = "")
plot(hclust(low.lat.pair$beta.sne, method = "average"), hang = -1, main = "", sub = "", xlab = "")
plot(hclust(low.lat.pair$beta.sor, method = "average"), hang = -1, main = "", sub = "", xlab = "")
```


# Dataset with Habitats as rows and taxa as columns -->  Medium latitude
## Checking the partitioning beta diversity (turnover + nestedness)

```{r}
med.lat <- med %>% 
  select(Order, Currentname, Isolationsource, lat_range) %>% 
  filter(Order != "", lat_range == "Medium") %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n_distinct(Isolationsource)) %>% spread(Currentname, N, fill = 0) %>% 
  column_to_rownames("Isolationsource")
  med.lat
  
med.lat.core <- betapart.core(med.lat) 
med.lat.core

med.lat.core.multij <- beta.multi(med.lat.core, index.family = "jaccard")
med.lat.core.multij
med.lat.core.multis <- beta.multi(med.lat.core, index.family = "sorensen")
med.lat.core.multis
```

# Dataset with Habitats as rows and taxa as columns -->  High latitude
## Checking the partitioning beta diversity (turnover + nestedness)

```{r}
 high.lat <- med %>%
  select(Order, Currentname, Isolationsource, lat_range) %>% 
  filter(Order != "", lat_range == "High") %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n_distinct(Isolationsource)) %>% spread(Currentname, N, fill = 0) %>% 
  column_to_rownames("Isolationsource")
  high.lat
  
high.lat.core <- betapart.core(high.lat) 
high.lat.core

high.lat.core.multij <- beta.multi(high.lat.core, index.family = "jaccard")
high.lat.core.multij
high.lat.core.multis <- beta.multi(high.lat.core, index.family = "sorensen")
high.lat.core.multis
```


```{r}
hab.taxa <- med %>%
  select(Order, Currentname, Isolationsource) %>% 
  filter(Order != "") %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n_distinct(Isolationsource)) %>% spread(Currentname, N, fill = 0) %>% 
  column_to_rownames("Isolationsource")
  hab.taxa

hab.taxa.core <- betapart.core(hab.taxa)

hab.taxa.core.multij <- beta.multi(hab.taxa.core, index.family = "jaccard")
hab.taxa.core.multij
hab.taxa.multis <-  beta.multi(hab.taxa.core, index.family = "sorensen")
hab.taxa.multis
```

