---
title: "summary_diversity"
author: "Vica"
date: "10/24/2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
---



```{r}
library(tidyverse)
library(RColorBrewer)
```

# Insert csv file and filter only countries included in the Mediterranean region

```{r, echo = FALSE, include=FALSE}
med <- read.csv("../Data/Med_cyano_list_20191024.csv", row.names = NULL)
med <- med %>% 
  filter(Med_border == "yes")
colnames(med)[1] <- "A/A"
med
```

#Number of distinct taxa in each Order, optimization in a barplot

```{r, echo=FALSE}
species_order_disti <- med %>% 
  filter(Order != "") %>%
  select(Order, Currentname) %>% 
  group_by(Order) %>% 
  summarize(Number_species = n_distinct(Currentname)) %>% 
  arrange(desc(Number_species))
species_order_disti

brewer.pal(n = 8, name = "Accent")
display.brewer.pal(n=8, "Accent")
sfm <- c("#7FC97F","#BEAED4","#FDC086","#FFFF99","#386CB0","#F0027F","#BF5B17","#666666")
sfm

species_order_disti_plot <- ggplot(species_order_disti, aes(x = reorder(Order, -Number_species), y = Number_species, fill = Order )) + geom_bar(stat = "identity") + theme_minimal() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45)) + geom_text(aes(label = Number_species)) 
species_order_disti_plot
  scale_fill_manual(values = c ("Synechococcales " = "#7FC97F","Nostocales" = "#BEAED4",
"Chroococales" = "#FDC086",
"Oscillatoriales" = "#FFFF99",
"Spirulinales" = "#386CB0",
"Pleurocapsales" = "#F0027F",
"Chroococcidiopsidales" = "#BF5B17",
"Gloeobacterales" = "#666666"))
```

#Number of taxa in each Order, optimization in a barplot

```{r,echo=FALSE}
species_order_all <- med %>% 
  filter(Order != "") %>%
  select(Order, Currentname) %>% 
  group_by(Order) %>% 
  summarize(Number_species = n())
species_order_all

species_order_all_plot <- ggplot(species_order_all, aes(x = reorder(Order, -Number_species), y = Number_species, fill = Order)) + geom_bar(stat = "identity") + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45)) + geom_text(aes(label = Number_species))
species_order_all_plot
```



```{r, echo=FALSE}
family_per_order <- med %>%
  filter(Family != "") %>% 
  select(Order, Family, Year)%>%
  group_by(Order, Family) %>% 
  summarize(N = n()) %>% 
  arrange(desc(N))
family_per_order

family_per_order_plot<- ggplot(family_per_order, aes( x = reorder(Order, -N), y = N, fill = Family)) + geom_bar(stat = "identity") + theme_minimal() +
  theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45))
family_per_order_plot

```


#Number of taxa in each Family, optimization in a barplot

```{r}
species_family_all <- med %>%
  filter(Family != "") %>% 
  select(Family, Currentname) %>%
  group_by(Family) %>% 
  summarize(Number_of_species = n()) %>% 
  arrange(desc(Number_of_species))
species_family_all <- head(species_family_all, 10) #Select the ten richest families

species_family_all_plot <- ggplot(species_family_all, aes(x = reorder(Family,-Number_of_species), y = Number_of_species, fill = Family)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 45)) + geom_text(aes(label = Number_of_species)) + theme(legend.position = "none")
species_family_all_plot
```

#Number of distinct taxa in each Family, optimization in a barplot

```{r}
species_family_disti <- med %>%
  filter(Family != "") %>% 
  select(Family, Currentname) %>%
  group_by(Family) %>% 
  summarize(Number_of_species = n_distinct(Currentname)) %>% 
  arrange(desc(Number_of_species))
species_family_disti <- head(species_family_disti, 10)

species_family_disti_plot <- ggplot(species_family_disti, aes(x = reorder(Family,-Number_of_species), y = Number_of_species, fill = Family)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 45)) + geom_text(aes(label = Number_of_species)) + theme(legend.position = "none")
species_family_disti_plot
```

#Number of  taxa in each Genus, optimization in a barplot

```{r}
species_genus_all <- med %>% 
  filter(Order != "") %>% 
  select(Genustotal, Currentname) %>% 
  group_by(Genustotal) %>% 
  summarize(Number_of_species = n()) %>% 
  arrange(desc(Number_of_species))
species_genus_all <- head(species_genus_all, 10)

species_genus_all_plot <- ggplot(species_genus_all, aes(x = reorder(Genustotal, - Number_of_species), y = Number_of_species, fill = Genustotal)) + geom_bar(stat = "identity")+ theme(axis.text.x = element_text(angle = 45)) + geom_text(aes(label = Number_of_species)) + theme(legend.position = "none")

species_genus_all_plot
```

#Number of distinct taxa in each Genus, optimization in a barplot

```{r}
species_genus_disti <- med %>% 
  filter(Order != "") %>% 
  select(Genustotal, Currentname) %>% 
  group_by(Genustotal) %>% 
  summarize(Number_of_species = n_distinct(Currentname)) %>% 
  arrange(desc(Number_of_species))
species_genus_disti <- head(species_genus_disti, 10)

species_genus_disti_plot <- ggplot(species_genus_disti, aes(x = reorder(Genustotal, - Number_of_species), y = Number_of_species, fill = Genustotal)) + geom_bar(stat = "identity")+ theme(axis.text.x = element_text(angle = 45)) + geom_text(aes(label = Number_of_species)) + theme(legend.position = "none")

species_genus_disti_plot
```

#Bar chart number of records in each Order
##Same as the second barplot

```{r, include=FALSE, cache=FALSE, echo=FALSE}
med_order <- med %>%
  filter(Order != "") %>% 
  select(Order, Family)%>%
  count(Order, sort = TRUE)
med_order


med_order_bar <- ggplot (med_order, aes(x = reorder(Order, -n), y = n)) + geom_bar(stat = "identity")+
  theme_classic() + theme(axis.text.x = element_text(angle = 45)) + theme(axis.line = element_line(size = 0.2, 
    linetype = "solid"), axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = NA), 
    panel.grid.minor = element_line(colour = NA), 
    axis.text = element_text(size = 12, colour = "black"), 
    panel.background = element_rect(fill = NA), 
    plot.background = element_rect(colour = NA), 
    legend.position = "none") +labs(x = NULL, y = NULL) + 
  theme(axis.text.x = element_text(angle = 45)) +
  theme(axis.text.x = element_text(vjust = 0.5))+ geom_text(aes(label = n), vjust = 1.6, color = "white", size = 3.5)

med_order_bar
ggsave("med_order_bar.png")
```

#Taxa found in habitat Pond

```{r}

pond.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>% 
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "Pond"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_records = n()) %>% 
  arrange(desc(Taxa_records))
pond.hab.taxa.disti

```

#Taxa found in habitat Lake

```{r}
lake.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "Lake"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_records = n()) %>% 
  arrange(desc(Taxa_records))
lake.hab.taxa.disti
```

#Taxa found in habitat Reservoir and Dam

```{r}
reserv.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter((str_detect(Isolationsource, pattern = c("Reservoir", "Dam")))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_records = n()) %>% 
  arrange(desc(Taxa_records))
reserv.hab.taxa.disti
```

#Taxa found in habitat River

```{r}
river.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "River"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_distinct = n_distinct(Currentname)) %>% 
  arrange(desc(Taxa_distinct))
river.hab.taxa.disti
```

#Taxa found in habitat Stream

```{r}
stream.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "Stream"))) %>% 
  group_by(Country,Isolationsource) %>% 
  summarise(Taxa_distinct = n_distinct(Currentname)) %>% 
  arrange(desc(Taxa_distinct))
stream.hab.taxa.disti
```



```{r}
spring.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "spring"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_distinct = n_distinct(Currentname)) %>% 
  arrange(desc(Taxa_distinct))
spring.hab.taxa.disti


spring.taxa <- med %>% 
  filter(Order != "") %>% 
  select(Currentname, Isolationsource, Order, Country) %>% 
  filter(str_detect(.$Isolationsource, c("Dam"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarize(T = n())
spring.taxa
```




```{r}
taxa.habitat <- split(med, med$Habitat_type)
taxa.habitat

unique.taxa.habitat <- sapply(taxa.habitat, function(x){
  unique(x["Currentname"])
})
unique.taxa.habitat
```



```{r}
med_currentname <- med %>%
  filter(Species != "")%>%
  select(Species, Currentname, Country)%>%
  group_by(Country)%>%
  summarize(Taxa_records = n())%>%
arrange(desc(Taxa_records))
med_currentname
```

##Unique Species in each country and barplot - NOT WORKING

```{r}
#vec <- as.vector(med$Currentname)
#unique_species <- names(which(table(vec) == 1))
#unique_species_df <- med[med$Currentname %in% unique_species,]

#unique_species_count <- unique_species_df %>% 
  #group_by(Country)%>%
  #summarize(Number_unique_species = length(Currentname))

#colourCount = length(unique(unique_species_count$Country))

        # make bars ordered
#unique_species_count$Country <- factor(unique_species_count$Country, 
                                #levels=unique_species_count$Country[order(unique_species_count$count, decreasing = T)])

#p <- ggplot(unique_species_count, aes(Country, unique_species_count)) +
        #geom_bar(stat="identity") +
        #theme_classic() + theme(legend.position = "none") + geom_text(aes(label=unique_species_count), vjust=1, colour = "white") +
  #theme(axis.text.x = element_text(angle = 45))
#p
#ggsave("p.png")
```


