---
title: "summary_diversity"
author: "Vica"
date: "10/24/2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
---



```{r echo=FALSE}
library(tidyverse)
library(RColorBrewer)
install.packages("compareDF")
library(compareDF)
```

# Insert csv file and filter only countries included in the Mediterranean region

```{r, echo = FALSE, include=FALSE}
med <- read.csv("../Data/Med_cyano_list_20191024.csv", row.names = NULL)
med <- med %>% 
  filter(Med_border == "yes")
colnames(med)[1] <- "A/A"
med <- med %>% 
  mutate(continent = case_when(Country %in% c("Greece", "Italy", "Spain", "France", "Albania", "Montenegro", "Slovenia", "Portugal", "Bulgaria", "Croatia") ~ "Europe",
                               Country %in% c("Egypt", "Morocco", "Tunisia", "Libya", "Algeria", "Israel","Lebanon") ~ "Africa",Country == "Turkey" ~ "Asia"))
```

#Number of distinct taxa in each Order, optimization in a barplot

```{r}
species_order_disti <- med %>% 
  filter(Order != "") %>%
  select(Order, Currentname) %>% 
  group_by(Order) %>% 
  summarize(Number_taxa = n_distinct(Currentname)) %>% 
  arrange(desc(Number_taxa))
species_order_disti


write.csv(species_order_disti, file = "Taxa_Order.csv") #Export the dataframe to a csv file


#brewer.pal(n = 8, name = "Accent")
#display.brewer.pal(n=8, "Accent")
#sfm <- c("#7FC97F","#BEAED4","#FDC086","#FFFF99","#386CB0","#F0027F","#BF5B17","#666666")
#sfm

species_order_disti_plot <- ggplot(species_order_disti, aes(x =reorder(Order, Number_species), y = Number_species, fill = Order )) + geom_bar(stat = "identity") + theme_classic() + theme(legend.position = "none") + geom_text(aes(label = Number_species)) 
species_order_disti_plot + coord_flip() + ylab("Number of taxa") + xlab("") +
scale_fill_manual(values = c (
"Synechococcales" = "#7FC97F",
"Nostocales" = "#BEAED4",
"Chroococcales" = "#FDC086",
"Oscillatoriales" = "#FFFF99",
"Spirulinales" = "#386CB0",
"Pleurocapsales" = "#F0027F",
"Chroococcidiopsidales" = "#BF5B17",
"Gloeobacterales" = "#666666"))

ggsave("species_order_disti_plot.png")
```

#Number of taxa in each Order, optimization in a barplot

```{r}
species_order_all <- med %>% 
  filter(Order != "") %>%
  select(Order, Currentname) %>% 
  group_by(Order) %>% 
  summarize(Number_species = n())
species_order_all

species_order_all_plot <- ggplot(species_order_all, aes(x =reorder(Order, Number_species), y = Number_species, fill = Order )) + geom_bar(stat = "identity") + theme_classic() + theme(legend.position = "none") + geom_text(aes(label = Number_species)) 
species_order_all_plot + coord_flip() + ylab("Number of records") + xlab("") +
  scale_fill_manual(values = c (
"Synechococcales" = "#7FC97F",
"Nostocales" = "#BEAED4",
"Chroococcales" = "#FDC086",
"Oscillatoriales" = "#FFFF99",
"Spirulinales" = "#386CB0",
"Pleurocapsales" = "#F0027F",
"Chroococcidiopsidales" = "#BF5B17",
"Gloeobacterales" = "#666666"))
```



```{r, echo=FALSE}
family_per_order <- med %>%
  filter(Family != "") %>% 
  select(Order, Family, Year)%>%
  group_by(Order, Family) %>% 
  summarize(N = n()) %>% 
  arrange(desc(N))
family_per_order


family_per_order_plot <- ggplot(family_per_order, aes(x =reorder(Order, N), y = N, fill = Family )) + geom_bar(stat = "identity") + theme_classic() + theme(legend.position = "none") 
family_per_order_plot + coord_flip() + ylab("Number of taxa") + xlab("")

```


#Number of taxa in each Family, optimization in a barplot

```{r}
species_family_all <- med %>%
  filter(Family != "") %>% 
  select(Order, Family, Currentname) %>%
  group_by(Order, Family) %>% 
  summarize(Number_of_species = n()) %>% 
  arrange(desc(Number_of_species))
species_family_all <- head(species_family_all, 20) #Select the ten richest families


species_family_all_plot <- ggplot(species_family_all, aes(x =reorder(Family, Number_of_species), y = Number_of_species, fill=Order )) + geom_bar(stat = "identity") + theme_classic() + theme(legend.position = "right") + geom_text(aes(label = Number_of_species)) 
species_family_all_plot + coord_flip() + ylab("Number of records") + xlab("") +
  scale_fill_manual(values = c (
"Synechococcales" = "#7FC97F",
"Nostocales" = "#BEAED4",
"Chroococcales" = "#FDC086",
"Oscillatoriales" = "#FFFF99",
"Spirulinales" = "#386CB0",
"Pleurocapsales" = "#F0027F",
"Chroococcidiopsidales" = "#BF5B17",
"Gloeobacterales" = "#666666"))
```

#Number of distinct taxa in each Family, optimization in a barplot

```{r}
species_family_disti <- med %>%
  filter(Family != "") %>% 
  select(Order, Family, Currentname) %>%
  group_by(Order, Family) %>% 
  summarize(Number_of_species = n_distinct(Currentname)) %>% 
  arrange(desc(Number_of_species))
species_family_disti <- head(species_family_disti, 20)


write.csv(species_family_disti, file = "Taxa_Family.csv")

species_family_disti_plot <- ggplot(species_family_disti, aes(x =reorder(Family, Number_of_species), y = Number_of_species, fill = Order )) + geom_bar(stat = "identity") + theme_classic() + theme(legend.position = "right") + geom_text(aes(label = Number_of_species)) 
species_family_disti_plot + coord_flip() + ylab("Number of taxa") + xlab("") +
  scale_fill_manual(values = c (
"Synechococcales" = "#7FC97F",
"Nostocales" = "#BEAED4",
"Chroococcales" = "#FDC086",
"Oscillatoriales" = "#FFFF99",
"Spirulinales" = "#386CB0",
"Pleurocapsales" = "#F0027F",
"Chroococcidiopsidales" = "#BF5B17",
"Gloeobacterales" = "#666666"))
ggsave("species_family_disti_plot.png")
```

#Number of  taxa in each Genus, optimization in a barplot

```{r}
species_genus_all <- med %>% 
  filter(Order != "") %>% 
  select(Order, Genustotal, Currentname) %>% 
  group_by(Order, Genustotal) %>% 
  summarize(Number_of_species = n()) %>% 
  arrange(desc(Number_of_species))
species_genus_all <- head(species_genus_all, 30)

species_genus_all_plot <- ggplot(species_genus_all, aes(x =reorder(Genustotal, Number_of_species), y = Number_of_species, fill = Order )) + geom_bar(stat = "identity") + theme_classic() + theme(legend.position = "none") + geom_text(aes(label = Number_of_species)) 
species_genus_all_plot + coord_flip() + ylab("Number of records") + xlab("") +
  scale_fill_manual(values = c (
"Synechococcales" = "#7FC97F",
"Nostocales" = "#BEAED4",
"Chroococcales" = "#FDC086",
"Oscillatoriales" = "#FFFF99",
"Spirulinales" = "#386CB0",
"Pleurocapsales" = "#F0027F",
"Chroococcidiopsidales" = "#BF5B17",
"Gloeobacterales" = "#666666"))
```

#Number of distinct taxa in each Genus, optimization in a barplot

```{r}
species_genus_disti <- med %>% 
  filter(Order != "") %>% 
  select(Order, Genustotal, Currentname) %>% 
  group_by(Order, Genustotal) %>% 
  summarize(Number_of_species = n_distinct(Currentname)) %>% 
  arrange(desc(Number_of_species))
species_genus_disti <- head(species_genus_disti, 28)

write.csv(species_genus_disti, file = "Taxa_genus.csv")


species_genus_disti_plot <- ggplot(species_genus_disti, aes(x =reorder(Genustotal, Number_of_species), y = Number_of_species, fill = Order )) + geom_bar(stat = "identity") + theme_classic() + theme(legend.position = "right") + geom_text(aes(label = Number_of_species)) 
species_genus_disti_plot + coord_flip() + ylab("Number of records") + xlab("") +
scale_fill_manual(values = c (
"Synechococcales" = "#7FC97F",
"Nostocales" = "#BEAED4",
"Chroococcales" = "#FDC086",
"Oscillatoriales" = "#FFFF99",
"Spirulinales" = "#386CB0",
"Pleurocapsales" = "#F0027F",
"Chroococcidiopsidales" = "#BF5B17",
"Gloeobacterales" = "#666666"))
ggsave("species_genus_disti_plot.png")
```

#Bar chart number of records in each Order
##Same as the second barplot

```{r}
med_order <- med %>%
  filter(Order != "") %>% 
  select(Order, Family)%>%
  count(Order, sort = TRUE)
med_order


med_order_bar <- ggplot (med_order, aes(x = reorder(Order, -n), y = n)) + geom_bar(stat = "identity")+
  theme_classic() + theme(axis.text.x = element_text(angle = 45)) + theme(axis.line = element_line(size = 0.2, 
    linetype = "solid"), axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = NA), 
    panel.grid.minor = element_line(colour = NA), 
    axis.text = element_text(size = 12, colour = "black"), 
    panel.background = element_rect(fill = NA), 
    plot.background = element_rect(colour = NA), 
    legend.position = "none") +labs(x = NULL, y = NULL) + 
  theme(axis.text.x = element_text(angle = 45)) +
  theme(axis.text.x = element_text(vjust = 0.5))+ geom_text(aes(label = n), vjust = 1.6, color = "white", size = 3.5)

med_order_bar
ggsave("med_order_bar.png")
```

#Taxa found in habitat Pond

```{r}

pond.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>% 
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "Pond"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_records = n()) %>% 
  arrange(desc(Taxa_records))
pond.hab.taxa.disti

#Select taxa in each Pond
pond.taxa <- med %>% 
  select(Order, Currentname, Isolationsource, Habitat) %>% 
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "Pond"))) %>%
  group_by(Isolationsource,Currentname) %>% 
  summarize(N=n())
pond.taxa

```

#Taxa found in habitat Lake

```{r}
lake.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(.,  pattern = "Lake"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_records = n()) %>% 
  arrange(desc(Taxa_records))
lake.hab.taxa.disti

#Select taxa in each Lake
lake.taxa <- med %>% 
  select(Order, Currentname, Isolationsource, Habitat) %>% 
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "Lake"))) %>%
  group_by(Isolationsource,Currentname) %>% 
  summarize(N=n())
lake.taxa


#Find common taxa between lake and pond Habitats
lake.pond <- intersect(pond.taxa$Currentname, lake.taxa$Currentname)
lake.pond
```
```{r}
setdiff(lake.taxa$Currentname, lake.pond)
```

#Taxa found in habitat Reservoir

```{r}
reserv.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter((str_detect(Isolationsource, pattern = "Reservoir"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_records = n_distinct(Currentname)) %>% 
  arrange(desc(Taxa_records))
reserv.hab.taxa.disti

```

#Taxa found in habitat River

```{r}
river.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "River"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_distinct = n_distinct(Currentname)) %>% 
  arrange(desc(Taxa_distinct))
river.hab.taxa.disti

```

#Taxa found in habitat Stream

```{r}
stream.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "Stream"))) %>% 
  group_by(Country,Isolationsource) %>% 
  summarise(Taxa_distinct = n_distinct(Currentname)) %>% 
  arrange(desc(Taxa_distinct))
stream.hab.taxa.disti


```



```{r}
spring.hab.taxa.disti <- med %>%  select(Currentname, Isolationsource, Order, Country) %>%
  filter(Order != "") %>% 
  filter_all(any_vars(str_detect(., pattern = "spring"))) %>% 
  group_by(Country, Isolationsource) %>% 
  summarise(Taxa_distinct = n_distinct(Currentname)) %>% 
  arrange(desc(Taxa_distinct))
spring.hab.taxa.disti


```

#Number of taxa in different Habitats

```{r}
habitat.taxa <- med %>% 
  select(Habitat, Currentname, Order) %>% 
  filter(Order != "") %>% 
  group_by(Habitat) %>% 
  summarize(N=n_distinct(Currentname)) %>% 
  arrange(desc(N))
habitat.taxa

habitat.taxa.plot <- ggplot(habitat.taxa, aes(x=reorder(Habitat,N), y = N, fill = Habitat)) + geom_bar(stat = "identity")+ theme_classic() + theme(legend.position = "none") + geom_text(aes(label = N)) 
habitat.taxa.plot + coord_flip() + ylab("Number of taxa") + xlab("") +
  scale_fill_brewer(palette = "Paired")
```

#Number of taxa in different Habitat types

```{r}
habitat.type.taxa <- med %>% 
  select(Habitat_type, Currentname, Order) %>% 
  filter(Order != "") %>% 
  group_by(Habitat_type) %>% 
  summarize(N=n_distinct(Currentname)) %>% 
  arrange(desc(N))
habitat.type.taxa <- habitat.type.taxa[-3,]

habitat.type.taxa.plot <- ggplot(habitat.type.taxa, aes(x=reorder(Habitat_type,N), y = N, fill = Habitat_type)) + geom_bar(stat = "identity")+ theme_classic() + theme(legend.position = "none") + geom_text(aes(label = N)) 
habitat.type.taxa.plot + coord_flip() + ylab("Number of taxa") + xlab("")
```




```{r}
taxa.habitat.type <- split(med, med$Habitat_type)
taxa.habitat

unique.taxa.habitat.type <- sapply(taxa.habitat.type, function(x){
  unique(x["Currentname"])
})


taxa.habitat <- split(med, med$Habitat)
taxa.habitat

unique.taxa.habitat <- sapply(taxa.habitat, function(x){
  unique(x["Currentname"])
})
unique.taxa.habitat.type
```



```{r}
med_currentname <- med %>%
  filter(Species != "")%>%
  select(Species, Currentname, Country)%>%
  group_by(Country)%>%
  summarize(Taxa_records = n_distinct(Currentname))%>%
arrange(desc(Taxa_records))
med_currentname


med_conts
```

#Different taxa in each Country, optimization in barplot 

```{r}
vec <- as.vector(med$Currentname)
unique_species <- names(which(table(vec) == 1))
unique_species_df <- med[med$Currentname %in% unique_species,]

unique_species_count <- unique_species_df %>% 
  group_by(Country, continent) %>% 
  summarize(Number_unique_species = length(Currentname))
unique_species_count

write.csv(unique_species_count, file = "Unique_species_per_Country.csv")

#colourCount = length(unique(unique_species_count$Country))


unique_species_count_plot <- ggplot(unique_species_count, aes(x=reorder(Country, Number_unique_species), y=Number_unique_species, fill = continent)) + geom_bar(stat="identity") + theme_classic() + theme(legend.position = "right") + geom_text(aes(label=Number_unique_species)) + coord_flip() + ylab("Number of taxa") + xlab("")
unique_species_count_plot
ggsave("unique_species_count_plot.png")
```

#Number of taxa in each Country, optimization in barplot

```{r}
taxa.disti <- med %>%
  filter(Species != "")%>%
  select(Species, Currentname, Country, continent)%>%
  group_by(Country, continent)%>%
  summarize(Taxa_number = n_distinct(Currentname))%>%
arrange(desc(Taxa_number))
taxa.disti

write.csv(taxa.disti, file = "Taxa_Country.csv")

taxa.disti.plot <- ggplot(taxa.disti, aes(x=reorder(Country, Taxa_number), y=Taxa_number, fill = continent)) + geom_bar(stat="identity") +
        theme_classic() + theme(legend.position = "right") + geom_text(aes(label=Taxa_number)) + coord_flip() + ylab("Number of taxa") + xlab("")
taxa.disti.plot
ggsave("taxa.disti.plot.png")
```





